---
title: "AHP"
author: "Yuqi Lou"
date: "21/07/2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Understanding User Preferences for social characteristics Features in IBM SkillsBuild Chatbot: Analysis using the Analytic Hierarchy Process (AHP)

```{r}
library(ahpsurvey)
library(magrittr)
library(pheatmap)

atts = c(
    'Proactivity', 'Conscientiousness', 'Damage control',
    'Thoroughness', 'Emotional intelligence', 'Identity',
    'Personality'
)

df = read.csv('C:/Users/louyu/D_AHP/extents.csv')
user_profiles = read.csv('C:/Users/louyu/D_AHP/user_profiles.csv')
```

```{r}
# AHP on every single row

data_ahp = df %>%
    ahp.mat(atts = atts, reciprocal = TRUE) # Converting negative numbers to reciprocal

eigentrue = ahp.indpref(data_ahp, atts, method = "eigen")

# Compute pairwise comparison matrices
data_matrix <- as.matrix(eigentrue)

pheatmap(data_matrix, 
         cluster_rows = FALSE,   # Set to TRUE if you want to cluster rows
         cluster_cols = TRUE,   # Set to TRUE if you want to cluster columns
         color = colorRampPalette(c("white", "black"))(100),
         main = "Overall preference of the Social Charateristic Features")
# Create the box plot
par(mar = c(10, 5, 4, 2) + 0.1)
boxplot(data_matrix, 
        main = "Overall preference of the Social Charateristic Features",
        ylab = "Values",
        las = 2)
```

```{r}
split_dataframe_by_column <- function(data_frame, user_prof, column_name) {
  # Get unique values of the specified column
  unique_values <- unique(user_prof[[column_name]])
  
  # Create an empty list to store the subsets
  dataframes_list <- list()
  
  # Split the data frame by the specified column and store subsets in the list
  for (value in unique_values) {
    indices = which(user_prof[[column_name]] == value)
    subset_df = data_frame[indices, ]
    dataframes_list[[as.character(value)]] <- subset_df
  }
  
  return(dataframes_list)
}
plot_heat_map = function(data_frame, user_profiles, column_name, column_full_name) {
  df_list = split_dataframe_by_column(data_frame, user_profiles, column_name)
  column_names = names(df_list)
  agg_ahps = c()
  
  for (value in column_names) {
    ahp_value = df_list[[value]] %>%
      ahp.mat(atts = atts, reciprocal = TRUE)
    
    eigentrue = ahp.indpref(ahp_value, atts, method = "eigen")
    agg = ahp.aggpref(ahp_value, atts, method = "eigen")
    
    data_matrix <- as.matrix(eigentrue)
    agg_ahps = rbind(agg_ahps, agg)
    
    if (nrow(eigentrue) == 1 & all(eigentrue[1, ] == eigentrue[1, 1])) {
      cat(paste("WARNING: there is only one rows of", value, "in", 
                  column_full_name, 
                  "\nand all columns have the same value.",
                  "\nThe heatmap is omitted due to R will output error in this case.",
                  "\nBut this row will show up in the", 
                  paste("\nPreferred Social Charateristic Features of different", column_full_name)))
      next
    }
    
    full_name_with_brakets = paste0("(", column_full_name, ")")
    pheatmap(data_matrix, 
             cluster_rows = FALSE,   # Set to TRUE if you want to cluster rows
             cluster_cols = FALSE,   # Set to TRUE if you want to cluster columns
             color = colorRampPalette(c("white", "black"))(100),
             main = paste("Preferred Social Charateristic Features of different", value, full_name_with_brakets))
    
  }
  
  rownames(agg_ahps) <- column_names
  data_matrix <- as.matrix(agg_ahps)
  pheatmap(data_matrix, 
           cluster_rows = FALSE,   # Set to TRUE if you want to cluster rows
           cluster_cols = FALSE,   # Set to TRUE if you want to cluster columns
           color = colorRampPalette(c("white", "black"))(100),
           main = paste("Preferred Social Charateristic Features of different", column_full_name))
}
plot_box_plot = function(data_frame, user_profiles, column_name, column_full_name) {
  df_list = split_dataframe_by_column(data_frame, user_profiles, column_name)
  column_names = names(df_list)
  all_values = c()  # Create a vector to store all data points
  group_labels = c()  # Create a vector to store group labels

  for (value in column_names) {
    ahp_value = df_list[[value]] %>%
      ahp.mat(atts = atts, reciprocal = TRUE)

    eigentrue = ahp.indpref(ahp_value, atts, method = "eigen")

    data_vector <- as.vector(eigentrue)
    all_values = c(all_values, data_vector)  # Concatenate data vectors
    group_labels = c(group_labels, rep(value, length(data_vector))) 
  }

  # Get the number of boxplots to be plotted
  num_plots <- length(column_names)

  # Create a vector of colors for the boxplots
  boxplot_colors <- rainbow(num_plots)

  par(mar = c(9, 5, 4, 2) + 0.1)
  # Create the boxplot with all data points
  boxplot(all_values,
          col = rep(boxplot_colors, each = ncol(eigentrue)),
          at = 1:(num_plots * ncol(eigentrue)),
          main = paste("Preferred Social Charateristic Features of different", column_full_name),
          ylab = "Values",
          # xlab = rep(names(eigentrue), each = num_plots),
          las = 2)

  # Add group labels to the x-axis 
  # xis(side = 1, at =  1:(num_plots * ncol(eigentrue)), 
  #     labels = rep(names(eigentrue), each = num_plots), las = 2)

  # Create the legend
  par(xpd = TRUE)
  legend("topright", legend = column_names, fill = boxplot_colors, bty = "n", inset = c(0, 0))

}

```

## AHP on Whether interacted with IBM Chatbot

AHP on Whether interacted with IBM SkillsBuild Chatbot is omitted since all participants answered yes.

## AHP on age

```{r}
plot_heat_map(df, user_profiles, "age", "age")
plot_box_plot(df, user_profiles, "age", "age")
```

## AHP on gender

```{r}
plot_heat_map(df, user_profiles, "gender", "gender")
plot_box_plot(df, user_profiles, "gender", "gender")
```

## AHP on Educational Background

```{r}
plot_heat_map(df, user_profiles, "edu", "Educational Background")
plot_box_plot(df, user_profiles, "edu", "Educational Background")
```

## AHP on Familiarity with emerging technologies

```{r}
plot_heat_map(df, user_profiles, "fam", "Familiarity with emerging technologies")
plot_box_plot(df, user_profiles, "fam", "Familiarity with emerging technologies")
```

## AHP on Frequency of Chatbot Usage

```{r}
plot_heat_map(df, user_profiles, "freq", "Frequency of using Chatbots")
plot_box_plot(df, user_profiles, "freq", "Frequency of using Chatbots")
```

## AHP on Overall satisfaction (IBM Chatbot)

```{r}
plot_heat_map(df, user_profiles, "sat", "Overall satisfaction (IBM Chatbot)")
plot_box_plot(df, user_profiles, "sat", "Overall satisfaction (IBM Chatbot)")
```
